The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-09 paper/ms.tex
Fixed plots in sec 3.3

Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer ($\vert \mu \vert > 
0.9$ $\&$ $\vert \mu \vert < 1.0]$).  We do not find any asymmetry in 
the line produced by the off-center emission, The difference
 between the profiles corresponding to the spheres located at $C=-0.5R$ 
 and that ones located at $C=0.5R$ is negligible.  As in the homogeneous / 
central model the line gets broader as the rotational velocity increase also 
the central part of the line becomes predominant . 
There is also a signature of possible three peaks profiles for some models ($\tau = 10^6,
V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) which would be studied 
in detail in the Sec.\ref{sec:3p}

@@

As mentioned in Sec\ref{sec:off-center} Off-centered emission shows signs of three peak 
profiles, to analyse this in more detail we use the same method of the spheres
explained in that section. We select spheres at $C=(\pm 0.25R, \pm0.5R, \pm0.75R)$ with a radii of
$0.25R$ for all the models, for those who present signs of three peak profiles such as 
$(V_{max}=50kms^{1}$ \& $\tau_{H}=10^{5}), (V_{max}=100kms^{1}$ \& $\tau_{H}=10^{6}), 
(V_{max}=200kms^{1}$ \& $\tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
with the aim of get a stronger profile.

>>>>

Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer ($\vert \mu \vert > 
0.9$ $\&$ $\vert \mu \vert < 1.0]$).  We do not find any asymmetry in 
the line produced by the off-center emission, The difference
 between the profiles corresponding to the spheres located at $C=-0.5R$ 
 and that ones located at $C=0.5R$ is negligible.  As in the homogeneous / 
central model the line gets broader as the rotational velocity increase also 
the central part of the line becomes predominant . 
There is also a signature of possible three peaks profiles for some models ($\tau = 10^6,
V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) which would be studied 
in detail in \S \ref{sec:3p}.

@@

As mentioned in \S \ref{sec:off-center} Off-centered emission shows signs of three peak 
profiles, to analyse this in more detail we use the same method of the spheres
explained in \S \ref{sec:off-center}. We select spheres at $C=(\pm 0.25R, \pm0.5R, \pm0.75R)$ with a radii of
$0.25R$ for all the models, for those who present signs of three peak profiles such as 
$(V_{max}=50kms^{1}$ \& $\tau_{H}=10^{5}), (V_{max}=100kms^{1}$ \& $\tau_{H}=10^{6}), 
(V_{max}=200kms^{1}$ \& $\tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
with the aim of get a stronger profile.
